Glyph-maps for visualizing climate data and models

### 2011-08-26 paper.tex
tweak intro

>>>>

Figure \ref{fig:glyphs} illustrates the idea of icon plots, with emphasis on temporal data. The time measurements are treated as variables in a multivariate data set. Here we have six years of monthly data, giving 72 time values which are considered to be 72 variables. Three different locations are selected, for demontration purposes. The top plot shows the time series of these three locations. Location ``1.1'' (red) has medium values of temperature, with strong seasonality, the six years corresponding to the six eaks. Location ``2.1'' (green) has generally high temperature values, with weaker seasonality in most years and a lack of low temperatures in the middle of the time period when lows would be expected. Location ``3.1'' (blue) has strong seasonality but generally low temperatures. The bottom plot shows these same cases as star glyphs. A separate glyph is created for each location. The 72 time variables form axes organized radially. Each temperature value is plotted relative to the overall range of temperature values. The seasonal patterns are clearly visible in this type of display, forming six ``petals'' in the icon. Location ``2.1'' has a different pattern than the other two, with only four petals, and location ``3.1'' is a much smaller ico indicating overall lower values.
